### 2022-05-16 readme.Rmd
update to readme

---
output:
  md_document:
    variant: gfm
---

@@

The approach uses quasi-random sampling to generate a quadrature
scheme based (e.g Berman & Turner 1992; Foster et al, 2018). Quasi-random 
sampling quadrature are form of spatially-balanced survey design or 
point stratification that aims to reduce the frequency of placing samples 
close to each other (relative to pseudo-random or grid designs). A quasi-random 
quadrature design improves efficiency of background point sampling 
(and subsequent modelling) by reducing the amount of spatial 
auto-correlation between data implying that each sample is providing as much 
unique information as possible (Grafston & Tille, 2013, Foster et al., 2018)
and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007).
Because the quasi-random design is not on a regular grid we use a Dirichlet 
tessellation to generate polygons for each point. Areal weights are then derived
from these polygons.

@@

@@

>>>>

---
output: github_document
---

@@

The approach uses quasi-random sampling (Grafston & Tille, 2013, Foster et al., 2018) to generate a quadrature scheme for numerical approximation of a Poisson point process model (Berman & Turner 1992; Warton & Shepard 2010). Quasi-random sampling quadrature are form of spatially-balanced survey design or point stratification that aims to reduce the frequency of placing samples close to each other (relative to pseudo-random or grid designs). A quasi-random quadrature design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013, Foster et al., 2018) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007). Because the quasi-random design is not on a regular grid we use a Dirichlet tessellation to generate polygons for each point. Areal weights are then derived from these polygons. Under this approach we **do not** use a targeted background scheme for generating 'pseudo-absences', but rather can account for bias in the sighting process
of presences using covariates or a offset when modelling (e.g Warton et al., 2013; Fithian et al, 2015).

@@

Renner, I.W., Elith, J., Baddeley, A., Fithian, W., Hastie, T., Phillips, S.J., Popovic, G. and Warton, D.I., 2015. Point process models for presence only analysis. Methods in Ecology and Evolution, 6(4), p.366-379.

@@

Warton, D.I., Renner, I.W. and Ramp, D., 2013. Model-based control of observer bias for the analysis of presence-only data in ecology. PloS one, 8(11), p.e79168.
